The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-01 albatros_paper.tex
HCC made a brand spanking new map of the island

\begin{figure}
  \begin{center}
    \includegraphics[width=0.5\linewidth]{Figures/site.PNG}
    \caption{{\bf UPDATE THIS FIGURE} Marion Island huts which are
      potential stations for the ALBATROS. The ring-like pattern is
      appropriate for imaging and produces a FWHM synthesized beam of
      8' at 5 MHz.}
    \label{Fig:marion}
  \end{center}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
    \caption{Marion Island huts which are
      potential stations for the ALBATROS. The ring-like pattern is
      appropriate for imaging and produces a FWHM synthesized beam of
      8' at 5 MHz.  {\bf add text here about which ones are huts vs current install sites}}
    \label{Fig:marion}
  \end{center}
\end{figure}
